---
title: "Creating a strange bird"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating a strange bird}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: oiseaux.bib
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(oiseaux)
```

## Goals

The goal of the `oiseaux` package [@borasky2022a] is to provide tools for
composers to manipulate bird calls for incorporation into musical 
compositions. `oiseaux` imports sound file download tools from `warbleR` [@araya_salas2017] and analysis / synthesis tools from `soundgen`
[@anikin2019].

In this vignette, we demonstrate `oiseaux` by creating a strange bird from
two well-known birds that are active at night in North America: the great
horned owl (Bubo virginianus) and the common loon (Gavia immer). The
resulting creature of the night is called the _owloon_.

## Acquiring the source media

We acquire data from [xeno-canto](https://xeno-canto.org/) using the
`oiseaux` function `download_usable_files`. 

```{r}

usable_owls <- oiseaux::download_usable_files(
  "Great Horned Owl",
  "~/owls"
) 
usable_loons <- oiseaux::download_usable_files(
  "Common Loon",
  "~/loons"
) 

```

## References
