---
title: "Creating a strange bird"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating a strange bird}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: oiseaux.bib
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(oiseaux)
library(dplyr)
library(warbleR)
library(soundgen)
```

## Goals

The goal of the `oiseaux` package [@borasky2022a] is to provide tools for
composers to manipulate bird calls for incorporation into musical 
compositions. `oiseaux` imports sound file download tools from `warbleR` [@araya_salas2017] and analysis / synthesis tools from `soundgen`
[@anikin2019].

In this vignette, we demonstrate `oiseaux` by creating a strange bird from
two well-known birds that are active at night in North America: the great horned owl (Bubo sss) and the common loon (). The resulting night creature is
called the _owloon_.

## Acquiring the source media

Since we're creating a new bird from owls and loons, we need to acquire some
suitable audio files. The `warbleR` package lets us query the
[zeno-canto](https://xeno-canto.org/), which is a collection of bird sounds
from around the world. Each sound file is licensed using one of the
[Creative Commons](https://creativecommons.org/share-your-work/) licenses.

Since we want to analyze and resynthesize the sounds, and will be using them
in compositions that may be recorded and published, we can't use files that
have Creative Commons licenses with the "ND" (no derivative works) or "NC"
(non-commercial) clause. That leaves us with "CC0" (public domain),
"CC-BY" (attribution), or "CC-BY-SA" (attribution / share-alike). It turns
out that most of the usable files are "CC-BY-SA", so that is the license we
use for the output files distributed with `oiseaux`.

## References
